A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2014-03-10 writeup/final revision/paper.tex
final version

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP}.

@@

A few languages standout for having suspiciously strong performance by out of region workers, notably Irish and Swedish, for which out of region workers account for a near equivalent volume and quality of translations to the in region workers. This is admittedly implausible, considering the relatively small number of Irish speakers worldwide, and the very low number living in the countries in which our Turkers were based (primarily India). Such results highlight the fact that cheating using online translation resources is a real problem, and despite our best efforts to remove workers using Google Translate, some cheating is still evident. Restricting to within region workers is an effective way to reduce the prevalence of cheating. We discuss the languages which are best supported by true native speakers in section 6.

@@

>>>>

\section{Background and Related Work}
Amazon's Mechanical Turk (MTurk) is an online marketplace for work that gives employers and researchers access to a large, low-cost workforce. MTurk allows employers to provide micro-payments in return for workers completing micro-tasks.  The basic units of work on MTurk are called `Human Intelligence Tasks' (HITs).  MTurk was designed to accommodate tasks that are difficult for computers, but simple for people. This facilitates research into human computation, where people can be treated as a function call \cite{vonAhnThesis,Little2009,quinn-bederson:2011}.  It has application to research areas like human-computer interaction \cite{bigham-et-al:2010,bernstein-et-al:2010}, computer vision  \cite{sorkin-forsyth:2008,deng-et-al:2010,rashtchian:10}, speech processing \cite{marge:10,lane-EtAl:2010:MTURK,Parent-Eskenazi:2011,Eskenazi:2013:crowdsourcing-speech-book},  and natural language processing \cite{Snow2008,callisonburch-dredze:2010:MTURK,laws-scheible-schutze:2011:EMNLP,che.hcomp11}.

@@

A few languages stand out for having suspiciously strong performance by out of region workers, notably Irish and Swedish, for which out of region workers account for a near equivalent volume and quality of translations to the in region workers. This is admittedly implausible, considering the relatively small number of Irish speakers worldwide, and the very low number living in the countries in which our Turkers were based (primarily India). Such results highlight the fact that cheating using online translation resources is a real problem, and despite our best efforts to remove workers using Google Translate, some cheating is still evident. Restricting to within region workers is an effective way to reduce the prevalence of cheating. We discuss the languages which are best supported by true native speakers in section 6.

@@

\section{Acknowledgements}

 This material is based on research sponsored by a DARPA Computer Science Study Panel phase 3 award entitled ``Crowdsourcing Translation'' (contract D12PC00368). The views and conclusions contained in this publication are those of the authors and should not be interpreted as representing official policies or endorsements by DARPA or the U.S. Government.  This research was supported by the Johns Hopkins University Human Language Technology Center of Excellence and through gifts from Microsoft and Google.

The authors would like to thank the anonymous reviewers for their thoughtful comments, which substantially improved this paper, and of course, our many hard-working Turkers.
